Benchmarking KiCS2

### 2015-11-16 benchmarks/benchmark_papers/kics2/bench_kics2.tex
Benchmark implementation updated
Parallel benchmarks modified

\documentclass{article}

@@

These benchmarks are executed with the option ``\texttt{:set +parallel}''
and different run-time settings to influence the number
of threads used for the execution.

>>>>

\documentclass{scrartcl}

@@

These benchmarks are executed with different search strategy options
to evaluate the parallel strategy w.r.t.\ the number
of threads used for the execution.
